Scenario 2 - MPX in the EU

### 2022-11-07 MS3.Rmd
Included a visualization however have hidden it as not needed for MS 3

kable(data_dic,
      col.names = c("Data Type", 
                    "Description"),
      caption = "Data Dictionary"
      ) 
```

>>>>

kable(data_dic,
      col.names = c("Data Type", 
                    "Description"),
      caption = "Data Dictionary"
      ) 
```
```{r, include=FALSE}
euro_mpx_cases %>% 
  ggplot(., aes(x = EU_region, y = country_pop_2022, fill = EU_region)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  theme_minimal() +
  labs(title = "Total Population 2022 by Region", x = "", y = "Pop") +
  theme(axis.title = element_text(size = 14),
        axis.text = element_text(size = 8),
        axis.ticks.x = element_blank(),
        legend.title = element_blank(),
        legend.position = "none")
```
